---
title: "Demo"
author: "Eric Scott"
date: '2022-04-05'
output: html_document
---

# Introduction

In this demo, I'll just load some data, do a simple analysis, and make a plot.
Then, I can update the data and show how everything else, including text generated from in-line code, updates.

```{r include=FALSE}
library(tidyverse)
library(palmerpenguins)
library(equatiomatic)
library(broom)
library(car)
library(scales)
```


```{r}
penguins <- penguins %>% filter(!is.na(flipper_length_mm))
```


```{r echo=FALSE}
sample_n(penguins, 5) %>%
  knitr::kable(caption = "Table 1. Five random rows from the palmerpenguins dataset.")
```

The dataset contains measurements on many penguins.
I will use it to see how flipper length varies with body mass and sex using a regression.

### Regression equation:

$$
y = \beta_0 + \beta_1x_1 + \beta_2x_2 + \beta_3x_1x_2 + \epsilon 
$$

# Results

```{r include=FALSE}
m <- lm(flipper_length_mm ~ body_mass_g * sex, data = penguins)
res <- tidy(Anova(m))
# res$p.value[1] %>% scales::pvalue()
```

There was a significant relationship between flipper length and body mass (p < 0.001), and a significant effect of sex (p < 0.001), but no significant interaction (p = 0.542).


```{r echo=FALSE}
augment(m, se_fit = TRUE) %>% 
  ggplot(aes(x = body_mass_g, fill = sex, color = sex)) +
  geom_point(aes(y = flipper_length_mm), alpha = 0.5) +
  geom_ribbon(aes(ymin = .fitted - .se.fit, ymax = .fitted + .se.fit), alpha = 0.4, color = NA) +
  geom_line(aes(y = .fitted)) +
  labs(x = "body mass (g)",  y = "flipper length (mm)")
  
```


